An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-11-04 EconGrowth2.Rnw
Fixed Table and Figure references in the Appendix.

Figure~\ref{fig:LINEX_GDP_Lattice_Graph} compares LINEX model predictions to historical data.

@@

The 95\% confidence intervals associated with Figure~\ref{fig:CD_Scatter_Graph} 
are shown in Table~\ref{tab:CD_Params_Table}.

@@

The data in Table~\ref{tab:CD_Params_Table} is plotted in
Figure~\ref{CD_Params_Graph}.

@@

The 95\% confidence intervals associated with Figure~\ref{fig:CDq_Scatter_Graph} 
are shown in Table~\ref{tab:CDq_Params_Table}
and Figure~\ref{CDq_Params_Graph}.

>>>>

Figure~\ref{fig:LINEX_GDP_Lattice_Graph} compares LINEX model predictions to historical data.
**** Remove $x$ and $u$ lines. ****

@@

The 95\% confidence intervals associated with Figure~\ref{fig:CD_Scatter_Graph} 
are shown in Table~\ref{tab:CD_Parameters_No_Energy}.

@@

The data in Table~\ref{tab:CD_Parameters_No_Energy} is plotted in
Figure~\ref{fig:CD_Params_Graph}.

@@

The 95\% confidence intervals associated with Figure~\ref{fig:CDq_Scatter_Graph} 
are shown in Table~\ref{tab:CD_Parameters_With_Q}
and Figure~\ref{fig:CDq_Params_Graph}.
